---
title: "verificaMX-events: Auditable Security Events in Mexico"
author: "Lisette Lurker"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: flatly
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview

This report presents verified security events in Mexico derived exclusively from
official sources (e.g., SEDENA communiqués). No social-media reports, inferred
coordinates, or speculative data are included.

Verification levels used in this dataset:

| Level | Meaning |
|---|---|
| `verified_official` | Confirmed by an official government communiqué |
| `corroborated` | Confirmed by two or more independent credible sources |
| `unverified` | Single non-official source; included for completeness only |

---

## Load data

```{r load-data}
source("../scripts/load_events.R")

events <- load_events("../data/processed/events_verified.csv")
```

## Summary statistics

```{r summary}
cat("Total events:", nrow(events), "\n")
cat("Date range:", format(min(events$date)), "to", format(max(events$date)), "\n")
cat("\nEvents by verification level:\n")
print(table(events$verification_level))
cat("\nEvents by state:\n")
print(table(events$state))
```

## Event table

```{r event-table}
display_cols <- c(
  "event_id", "date", "municipality", "state",
  "event_type", "verification_level", "source_type"
)
knitr::kable(events[, display_cols], row.names = FALSE,
             caption = "Verified security events")
```

## Source auditability

The full original text is preserved for each event, enabling independent verification.

```{r source-text, results='asis'}
for (i in seq_len(nrow(events))) {
  cat(sprintf("\n### Event %s — %s, %s (%s)\n\n",
              events$event_id[i],
              events$municipality[i],
              events$state[i],
              events$date[i]))
  txt <- load_source_text(events$source_id[i],
                          raw_dir = "../data/raw")
  cat("```\n", txt, "\n```\n\n", sep = "")
}
```

## Methodology notes

- Only official communiqués and corroborated reports are included.
- Geographic information is taken directly from source text; no coordinates are
  inferred from maps or third-party databases.
- Each event links to a `source_id` that maps to a file in `data/raw/`.
- This report is fully reproducible: re-knitting this document from the raw data
  will produce identical results.
